\linksection{layout}{Project Layout}
\begin{itemize}[itemsep=0pt]
    \item \mono{tests/} outside of \mono{src/}, file layout 1:1 mirroring (roughly) of \mono{src/mypackage/}
    \item \mono{conftest.py}: fixtures, plugin hooks, etc.
    \item \mono{pytest.ini}/\mono{pyproject.toml}/\ldots{}: config
    \item \mono{__init__.py} files in \mono{src/myproject} and \mono{tests/}
\end{itemize}

\newcommand{\dinit}{\_\_init\_\_.py}

\vspace{-.5em}
\begin{minipage}{.45\linewidth}
    \footnotesize
    \dirtree{%
        .1 myproject/.
        .2 \textcolor{gray}{pytest.ini}.
        .2 pyproject.toml.
        .2 src/myproject/.
        .3 \dinit.
        .3 utils.py.
        .3 export/.
        .4 \dinit.
        .4 jsonexport.py.
        .4 yamlexport.py.
        .2 \highlightbox{tests/}.
        .3 \codeskip*.
    }
\end{minipage}
\begin{minipage}{.49\linewidth}
    \footnotesize
    \dirtree{%
        .1 \highlightbox{tests/}.
        .2 \dinit.
        .2 conftest.py.
        .2 test\_utils.py.
        .2 export/.
        .3 \dinit.
        .3 conftest.py.
        .3 test\_jsonexport.py.
        .3 test\_yamlexport.py.
    }
\end{minipage}
\vspace{-1em}

\linksection{config}{Configuration}
\begin{itemize}[itemsep=0pt]
    \item \inisec{[pytest]} in (\mono{.})\mono{pytest.ini}
    \item pytest 9+: \inisec{[pytest]} in (\mono{.})\mono{pytest.toml}
    \item \inisec{[tool.pytest.ini_options]} in \mono{pyproject.toml}
    \item pytest 9+: \inisec{[tool.pytest]} in \mono{pyproject.toml}
    \item \inisec{[pytest]} in \mono{tox.ini}
    \item \inisec{[tool.pytest]} in \mono{setup.cfg} (deprecated)
\end{itemize}

%\section{CLI vs. config}
%
%\begin{minipage}{.52\linewidth}
%Set config opts from CLI: \\
%\monot{pytest~\highlightbox{-o option=value}}
%\end{minipage}
%\begin{minipage}{.47\linewidth}
%Set CLI opts from config: \\
%\ini{addopts = ...} \\ (use \inikey{testpaths} for paths)
%\end{minipage}

\vspace{-1.5em}
\linksubsection{strict}{Strict Mode}
pytest 9: \ini{strict = true} enables: \vspace{-.5em}

\begin{itemize}[itemsep=0pt]
    \item \inikey{strict_config} (error on unknown options)
    \item \inikey{strict_markers} (error on unknown markers)
    \item \inikey{strict_parametrization_ids} \\ (error on duplicate test IDs)
    \item \inikey{strict_xfail} (error on unexpected passes)
\end{itemize}

Older pytest versions: Set \ini{xfail_strict = true} and \ini{addopts = --strict-config --strict-markers}

